HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-17 paper/main.tex
some edits to intro

These problems were partially addressed by measures that decompose over sub-parts of the evaluated
translation sentence (henceforth, {\it translation}),
most commonly over its words or n-grams,
quantifying the overlap of its sub-parts relative a reference translation.
More recent work on MT evaluation proposed measures
that decompose over semantically defined units,
quantifying the similarity of the output and the reference in terms of
their verb argument structure; the most notable of these measures is
HMEANT \cite{lo2011structured}.
While allowing to localize semantic errors in the translation,
these measures' focus on verb argument structures misses out on many pervasive semantic phenomena,
such as inter-clause linkage and nominal argument structures, and thus only provides
a limited perspective on the semantic similarity between the output and reference.
Moreover, assigning semantic structure to MT output, especially when low in quality,
is difficult and arguably ill-defined.

@@

We conduct experiments with four language pairs: English-German, English-Polish,
English-Romanian and English-Czech, and report efficiency (time of annotation) and
inter-annotator agreement scores, as well as qualitative comparison of the resulting
HUME scores with crowd-sourced adequacy judgements. The results show that HUME obtains 
agreement scores which are on par with those of standard sentence-level ranking measures,
but unlike them, HUME's scores do not decrease with longer sentences.\bh{We may
  have to focus more on qualitative aspects, if we just try to sell
  the measure on IAA, then the figures are not stunning.}
The paper concludes by outlining ongoing work to construct semi- and
fully-automatic variants of HUME.

>>>>

These problems were partially addressed by measures that decompose over sub-parts of the evaluated
translation sentence (henceforth, {\it translation}),
most commonly over its words or n-grams,
quantifying the overlap of its sub-parts relative a reference translation.
More recent work on MT evaluation proposed measures
that decompose over semantically defined units,
quantifying the similarity of the output and the reference in terms of
their verb argument structure; the most notable of these measures is
HMEANT \cite{lo2011structured}.
These measures can localize semantic errors in the translation, but
their focus on verb argument structures misses many pervasive semantic phenomena
(such as inter-clause linkage and nominal argument structures) and thus they only provide
a limited perspective on the semantic similarity between the output and reference.
Moreover, assigning semantic structure to MT output, especially when low in quality,
is difficult and arguably ill-defined.

@@

We conduct experiments with four language pairs: English-German, English-Polish,
English-Romanian and English-Czech, and report efficiency (time of annotation) and
inter-annotator agreement scores, as well showing how HUME can address a range of 
semantic phenomena\bh{Do we?}. The results show that HUME obtains 
agreement scores which are on par with those of standard sentence-level ranking measures,
but unlike them, HUME's scores do not decrease with longer sentences.
The paper concludes by outlining ongoing work to construct semi- and
fully-automatic variants of HUME.
